Analysis

### 2021-01-28 analysis.Rmd
looked at missingness in the denomination variable

```{r cache = TRUE}
library("naniar")
vis_miss(df) # substantial pattern of missing ness in a few variables, 
```

@@

### Dag shoes two adjustment sets
```{r}
tidy_ggdag2 <- dagify(
  wb  ~ support + ses + male + country + U2,
  support ~ church + male + country,
  church ~ age + male + country + U1,
  ses ~ country + age + U2,
  exposure =  "church",
  outcome =   "wb"
) %>%
  tidy_dagitty()

@@

```{r}
# get data into shape
d1 <- df %>%
  dplyr::filter(
    !is.na(wb_psychANXIETY),!is.na(age),!is.na(rel_CHURCHFREQ),!is.na(wb_psychMEANING),!is.na(male),!is.na(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::mutate(
    anx = as.numeric(wb_psychANXIETY),
    anx_s = scale(wb_psychANXIETY),
    #put outcome in ST units (see McElreath 2021)  # not necessary
    age_s = scale(age),
    ch = rel_CHURCHFREQ,
    mn  = wb_psychMEANING,
    bg =  rel_EXTENTBELIEVEGOD,
    ch_s = scale(rel_CHURCHFREQ),
    mn_s = scale(wb_psychMEANING),
    bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx, ch, mn, bg, anx_s, age_s, ch_s, mn_s, male2, country, male, bg_s,wb_psychANXIETY)

>>>>

```{r cache = TRUE}
library("naniar")
vis_miss(df) # substantial pattern of missing ness in a few variables, 
gg_miss_upset(df)
```

@@

### Dag shoes two adjustment sets both of which contain denomination
```{r}
tidy_ggdag2 <- dagify(
  wb  ~ support + ses + male + country + U2,
  support ~ church + male + country + den,
  church ~ age + male + country + den + U1,
  ses ~ country + age + U2,
  exposure =  "church",
  outcome =   "wb"
) %>%
  tidy_dagitty()

@@

```{r}
# get data into shape
d1 <- df %>%
  dplyr::filter(
    !is.na(wb_psychANXIETY),!is.na(age),!is.na(rel_CHURCHFREQ),!is.na(wb_psychMEANING),!is.na(male),!is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.numeric(wb_psychANXIETY),
    anx_s = scale(wb_psychANXIETY),
    #put outcome in ST units (see McElreath 2021)  # not necessary
    age_s = scale(age),
    ch = rel_CHURCHFREQ,
    mn  = wb_psychMEANING,
    bg =  rel_EXTENTBELIEVEGOD,
    ch_s = scale(rel_CHURCHFREQ),
    mn_s = scale(wb_psychMEANING),
    bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx, ch, mn, bg, anx_s, age_s, ch_s, mn_s, male2, country, male, bg_s,wb_psychANXIETY)
